### 2023-04-12 paper-thesis/chapters/01-introduction.tex
Minor improvements to the thesis

\section*{Contributions}
The primary contribution of this thesis is to investigate how well Statix is fit for the task of defining a dependently-typed language. The goal is not only to show that Statix can implement it, but also that the implementation is more concise than in a general purpose language. We will start by implementing the Calculus of Constructions~\cite{Coquand_Huet_1988}, a lambda calculus with dependent types, as this is one of the most simple dependently typed languages (chapter~\ref{chap:baselang}).

However, this language is not very practical to write actual complex programs in, so to improve this situation we will extend the language with typical features of dependently typed languages. We will provide the following additional contributions:
\begin{itemize}
	\item We show the language is easily extendable, by extending it with booleans among other features (chapter~\ref{chap:bools}).
	\item We show how to add inference of implicit arguments to the implementation (chapter~\ref{ch:inference}).
	\item We show how to add support for inductive datatypes to the implementation (chapter~\ref{ch:datatypes}).
	\item We show how to add support for universes to the implementation (chapter~\ref{ch:universes}).
\end{itemize}

>>>>

\section*{Contributions}
The primary contribution of this thesis is to investigate how well Statix is fit for the task of defining a dependently-typed language. The goal is not only to show that Statix can implement it, but also that the implementation is more concise than in a general purpose language (\textbf{Research Question 1}). We will start by implementing the Calculus of Constructions~\cite{Coquand_Huet_1988}, a lambda calculus with dependent types, as this is one of the most simple dependently typed languages (chapter~\ref{chap:baselang}).

However, this language is not very practical to write actual complex programs in, so to improve this situation we will extend the language with typical features of dependently typed languages. We will provide the following additional contributions:
\begin{itemize}
	\item \textbf{RQ2:} We show the language is easily extendable, by extending it with booleans among other features (chapter~\ref{chap:bools}).
	\item \textbf{RQ3:} We show how to add inference of implicit arguments to the implementation (chapter~\ref{ch:inference}).
	\item \textbf{RQ4:} We show how to add support for inductive datatypes to the implementation (chapter~\ref{ch:datatypes}).
	\item \textbf{RQ5:} We show how to add support for universes to the implementation (chapter~\ref{ch:universes}).
\end{itemize}

### 2023-04-12 paper-thesis/chapters/99-conclusion.tex
Minor improvements to the thesis

\paragraph{RQ4: Can we add support for inductive data types to the implementation?}
chapter~\ref{ch:datatypes} adds support for inductive data types with parameters and indices. We give steps for type-checking data type declarations. Additionally, we give each data type an eliminator and show how to type-check and beta reduce eliminators. Finally, we show that positivity checking can be implemented concisely.

>>>>

\paragraph{RQ4: Can we add support for inductive data types to the implementation?}
Chapter~\ref{ch:datatypes} adds support for inductive data types with parameters and indices. We give steps for type-checking data type declarations. Additionally, we give each data type an eliminator and show how to type-check and beta reduce eliminators. Finally, we show that positivity checking can be implemented concisely.
